Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-06-01 manuscript.Rmd
Edits to Syria in Context section

## Syria in context
The decades prior to the onset of the Arabs Spring in Syria were marked by
social repression and fear. In 1971, Hafez al-Assad overthrew the previous
leader and remained in power for thirty years, presiding during times of
regional contentiousness and cooperation until his death in 2000. His son,
Bashar al-Assad, who continued the regime of authoritarian leadership, assumed
his office. The Assad lineage hails from a minority Islamic sect, the Alawites,
in a multi-religious and multi-ethnic country comprised of Christians, Sunni and
Shia Muslims, Kurds, and Palestinian refugees.

@@

Following a wave of democratization efforts across the Middle East and North
Africa, protests began modestly in Syria in March 2011. The regime responded
harshly with imprisonments, detentions, censorship, and military operations as
the resistance to Assad’s regime grew and spread throughout the country. The
fighting escalated in earnest in March 2012, after increased unrest in the
western city of Homs. International actors, including the Red Cross/Red Crescent
Society, the United Nations General Assembly, the Security Council, and
individual leaders throughout the world worked toward cease-fires, negotiations,
and concessions, without much success. While many high-level military and
diplomatic officials have defected from the regime, sufficient loyal forces have
been able to execute continued repression. During this time between March and
June 2012, more than eight million tweets were sent within Syria revealing the
details of the conflict.

Syria is a multi-ethnic, multi-lingual, and multi-religious state. Kurdish
people comprise between 10-15% of the population, Alawites between 8-15%,
Christians about 10%. There are also much smaller sects, i.e. the Ismailis and
Druze, but Sunni Muslims comprise the vast majority of society, and most people
speak Arabic as their mother tongue. Most policy reports addressing the current
conflict report on the cohesion of the ruling Alawite military elite, rather
than on the cohesiveness of the opposition movement. However, the Sunni
majority’s disaffection with the Syrian government and lack of political
representation provide sufficient grievance and collective group identification
to make them a cohesive force.

>>>>

## Syria in Context
The decades preceding the Arab Spring in Syria were marked by
social repression and fear. In 1971, Hafez al-Assad overthrew the previous
leader and remained in power for thirty years, presiding during
regional contentiousness and cooperation until his death in 2000. His son,
Bashar al-Assad continued the regime of authoritarian leadership as he assumed
his office. The Assad lineage hails from a minority Islamic sect (the Alawites)
in a multi-religious and multi-ethnic country comprising Christians, Sunni and
Shia Muslims, Kurds, and Palestinian refugees.

@@

Following a wave of democratization efforts across the Middle East and North
Africa, modest Syrian protests began in March 2011. The regime responded
harshly with imprisonments, detentions, censorship, and military operations as
the resistance to Assad’s regime grew and spread throughout the country. The
fighting escalated dramatically in March 2012, after increased unrest in the
western city of Homs. International actors---including the Red Cross/Red Crescent
Society, the United Nations General Assembly, the Security Council, and
individual world leaders---worked toward cease-fires, negotiations,
and concessions without much success. While many high-level military and
diplomatic officials defected from the regime, numerous loyal forces
continued the regime's repression, and the Syrian people turned to social
media to help coordinate their activism and communicate to the world. Between March and
June 2012, more than 8 million tweets were sent within Syria, revealing the
details of the conflict suppressed by the government.

Syria is a multi-ethnic, multi-lingual, and multi-religious state. Kurdish
people make up between 10-15% of the population, Alawites between 8-15%,
Christians about 10%. There are also much smaller sects (e.g., Ismailis,
Druze), but Sunni Muslims comprise the vast majority of society. Most people
speak Arabic as their primary language. Most policy reports addressing the current
conflict report on the cohesion of the ruling Alawite military elite, rather
than on the cohesiveness of the opposition movement. However, the Sunni
majority's disaffection with the Syrian government and their lack of political
representation provide sufficient grievance and collective group identification
to make them a cohesive force.
